---
title: "Forest_cover_Data"
author: "Durga Gaddam"
date: "November 21, 2016"
output: html_document
---

###Objective
The main objective of this project is to visualize the data of forest cover type provided by kaggle and predict the cover type from the train data set provided.

This is a classification problem, We can use any of the following classification algorithms

1) Decision Trees
2) Random Forests
3) Support Vector Machines
4) Neural Networks
5) K Nearset Neighbour 
6) Naive Bayes 
7) XGBoost


library(data.table)
library(dplyr)
install.packages("moments")
library(moments)
install.packages("PerformanceAnalytics")
library(PerformanceAnalytics)
library(ggthemes)
library(ggplot2)
library(RColorBrewer)
library(vioplot)
install.packages("vioplot")
install.packages("xgboost")
setwd("F:/R PRACTICE/ForestCover")
```{r}
require(data.table)
require(ggplot2)
require(moments)
require(xgboost)
train <- fread("train.csv", stringsAsFactors = FALSE) 
train <- train[, Id:=NULL, ]
train <- train[, Soil_Type15:=NULL]
train <- train[, Soil_Type7:=NULL]
test <- fread("test.csv", header = TRUE, stringsAsFactors = FALSE )
test <- test[, Id:=NULL]

is.data.table(train)
names(train)

```

Here the Cover_Type is the outcome variable that we are interested in.

```{r}
dim(train)
str(train)
summary(train)

skewness(train)

table(train$Cover_Type)
```

Since Wilderness_Area and Solid_type are both binary we remove those features for correlation.

```{r}

ggplot(train, aes(Hillshade_9am, Hillshade_3pm ))+
        geom_point(aes(colour= as.factor(Cover_Type)))+scale_color_brewer(palette="Set1")

ggplot(train, aes(Horizontal_Distance_To_Hydrology,Vertical_Distance_To_Hydrology))+ geom_point(aes(colour= as.factor(Cover_Type)))+ scale_color_brewer(palette="Set1")

ggplot(train, aes(Aspect, Hillshade_3pm ))+
        geom_point(aes(colour= as.factor(Cover_Type)))+scale_color_brewer(palette="Set1")

ggplot(train, aes(Hillshade_Noon, Hillshade_3pm ))+
        geom_point(aes(colour= as.factor(Cover_Type)))+scale_color_brewer(palette="Set1")


ggplot(train, aes(Slope, Hillshade_Noon))+
        geom_point(aes(colour= as.factor(Cover_Type)))+scale_color_brewer(palette="Set1")


ggplot(train, aes(Aspect, Hillshade_9am))+
        geom_point(aes(colour= as.factor(Cover_Type)))+scale_color_brewer(palette="Set1")


ggplot(train, aes(Elevation,Horizontal_Distance_To_Roadways))+
        geom_point(aes(colour= as.factor(Cover_Type)))+scale_color_brewer(palette="Set1")

xm <- names(train)
xm

for (i in 1:54)
{
print(ggplot(train, aes_string(x=train$Cover_Type, y=xm[i]))+xlab("Cover_Type") + geom_violin(aes(fill= as.factor(Cover_Type))))
        
}
```
###Prediction

```{r}
which(lapply(train, sd)==0)
train <- as.data.frame(train)
train <- scale(train, center = TRUE)
head(train)


require(randomForest)
class(train)

names(train)
train <- as.data.table(train)
model.random <- randomForest(as.factor(Cover_Type)~., train)
varImpPlot(model.random)
test$Cover_Type <- predict(model.random, test, class= "type")

head(test$Cover_Type)

```
